MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-04-26 Article.tex
increase font of mpi plots
describe more MPI impl, fix MPI figure captions

MaBoSS.MPI is a straightforward extension of the original MaBoSS CPU code to the MPI programming interface.
Briefly, each thread is assigned to compute a single trajectory at once, progressively collecting the results into a privatized hashmap-based statistics aggregation structure. The total amount of trajectory tasks is evenly split among the MPI nodes, adding a second layer of parallelism.

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{plots/sizek_mpi.pdf}
\caption{Scalability results of MPI implementation on Sizek model with 20 cores per MPI node.}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{plots/synth_mpi_speedup.pdf}
\caption{Speedup scaling of MPI implementation on a synthetic model with 1000 nodes and 32 cores per MPI node.}
\label{fig:synthetic_results}
\end{figure}

>>>>

MaBoSS.MPI is a straightforward extension of the original MaBoSS CPU code to the MPI programming interface.
Briefly, each MPI node is assigned to simulate the same number of trajectories (up to a remainder). These are further uniformly distributed among the CPU cores of the node, each thread progressively collecting the results into a privatized hashmap-based statistics aggregation structure.

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{plots/sizek_mpi.pdf}
\caption{Scalability results of MPI implementation on Sizek model with up to 192 MPI nodes and 20 cores per node, summing up to 3840 cores.}
\label{fig:sizek_results}
\end{figure}

@@

\begin{figure}%[tbhp]
\centering
\includegraphics[width=3.25in]{plots/synth_mpi_speedup.pdf}
\caption{Speedup scaling of MPI implementation on a synthetic model with 1000 nodes, running on up to 192 MPI nodes with 32 cores per MPI node, summing up to 6144 cores.}
\label{fig:synthetic_results}
\end{figure}
